Missing links, false positives, and the topological robustness of predicted food webs

### 2022-02-28 manuscript/ms_C3.Rmd
minor changes

AG: I will also add robustness plot for random extinction. It takes more time to compute.

@@

The findings from our study is similar to what had been documented for other food web models [@dunneCascadingExtinctionsCommunity2009], in terms of increase in the robustness when the connectance of the food web is increased. A future study could be to understand the robustness of other food web models [@InferringFoodWeb] and compare it with our study. We expect similar results.

@@

Need to coordinate this content with what I proposed on line 141.

Line 141 is "Include here the possibility that the increased connectance would influence dynamical stability, and state if and why this may increase or decrease stability."

>>>>

AG: I will also update the robustness plot for random extinction (Fig. 4 (b)) once the simulation is completed. The one shown here is only for few simulations and as a placeholder. It takes more time to compute.

@@

The findings from our study is similar to what had been documented for other food web models [@dunneCascadingExtinctionsCommunity2009], in terms of increase in the robustness when the connectance of the food web is increased. A future study could be to understand the robustness of other food web models [@gravelInferringFoodWeb2013a] and compare it with our study. We expect similar results.

@@

<!-- Need to coordinate this content with what I proposed on line 141. -->

<!-- Line 141 is "Include here the possibility that the increased connectance would influence dynamical stability, and state if and why this may increase or decrease stability." -->
